\documentclass[11pt,letterpaper,roman]{moderncv}
\usepackage[scale=0.8,margin=0.65in]{geometry}
\usepackage{fontspec} 

% \setmainfont[Ligatures=TeX,
%              Numbers=OldStyle]{IBM Plex Sans}

\moderncvstyle{classic}
\moderncvcolor{blue}

\name{Robert}{Herley IV}
\title{Software Engineer $\cdotp$ Full Stack Developer}
\address{28 Pioneer Blvd}{Huntington Station, NY 11746}
\phone[mobile]{1-631-896-7161}
\email{robherley13@gmail.com}
\homepage{robherley.xyz}
\social[linkedin]{robherley}
\social[github]{robherley}

\begin{document}

\makecvtitle

\sethintscolumntowidth{mmm yyyy - mmm yyyy}

\section{Education}
\cventry{2015 -- Current}{B.S. Computer Science}{Stevens Institute of Technology}{Hoboken, NJ}{}{
    \textit{Major GPA: 3.91, Overall GPA -- 3.78}
    \begin{itemize}
        \item Vice President of Upsilon Pi Epsilon (Computer Science Honor Society)
        \item Secretary of Stevens Computer Science Club
        \item Teaching Assistant for CS146 Intro to Web Development and CS546 Web Programming
        \item Dean's List: 2016 - 2018
        \item Graduation - May 2019
    \end{itemize}
}

\section{Experience}
\cventry{June 2017 -- Current}{Software Engineer}{\href{https://ibm.com}{IBM}}{Armonk, NY}{}{
    \begin{itemize}
        \item Designed and developed two applications: Overcast (web dashboard for PaaS metrics) and Kommodore (Kubernetes monitoring tool) for IBM Cloud Dedicated.
        \item Applications were implemented with React/Redux (frontend) and Express/NodeJS (backend) and containerized as deployments in Kubernetes.
        \item PostgreSQL, MongoDB and Redis were utilized for persistant and ephermal storage.
        \item Practiced Agile methodology with daily scrums and iteration planning with Trello.
    \end{itemize}
}
\cventry{Jan 2017 -- June 2017}{Software Engineer}{\href{http://onsightdigitalsolutions.com/}{OnSight Digital Solutions}}{Hoboken, NJ}{}{
    \begin{itemize}
        \item Developed an online service that organizes transaction information from internal APIs to an end-user.
        \item Implemented technologies front-end technologies: Bootstrap, D3.js and LESS.
        \item Undertow Java back-end deployed in AWS, managed mySQL database in DataGrip.
    \end{itemize}
}

\section{Projects}
\cventry{Academic}{Yet Another Messaging Service}{}{}{}{
    \begin{itemize}
        \item Slack-like clone written in Typescript and React, and Electron for the client.
        \item Socket.io was used for message communication, and MongoDB for persistant storage. 
    \end{itemize}
}
\cventry{Academic}{Stratus}{}{}{}{
    \begin{itemize}
        \item Online Markdown editor web service written in React/Redux.
        \item MongoDB was used for users storage and mappings of files to an Amazon S3 bucket.
    \end{itemize}
}

\cventry{Hackathon}{Scramble}{}{}{}{
    \begin{itemize}
        \item Collection of fast-paced multiplayer mini-games in the browser, written in React.
        \item Express.js server pairs clients into Socket.io Rooms and starts a random mini-game between the two clients.
        \item HackBU Winner - Best Design
    \end{itemize}
}

\section{Skills}
\cvitem{\textbf{Languages}}{JavaScript/TypeScript, C/C++, Python, Java, Bash, SQL, Go}
\cvitem{\textbf{Web \& Cloud}}{HTML5, CSS/Sass, React/Redux, MongoDB, Docker, Kubernetes, Electron}
\cvitem{\textbf{Misc. Tech}}{Git, Linux, Redis, Travis CI, Trello, ZenHub, \LaTeX{}}


\end{document}
